---
name: Ryan P. O'Donnell
date: "`r format(Sys.time(), '%B, %Y')`"
position: PhD Student
address: Research School of Biology, Australian National University
phone: +61 422 289 005
email: ryan.odonnell@anu.edu.au
website: rpodonnell.github.io
github: rpodonnell
linkedin: rpodonnell
twitter: rpodonnell_
headcolor: "414141"
fontawesome: yes
fontsize: 10
output: 
  vitae::awesomecv:
    keep_tex: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(ggplot2)
library(dplyr)
library(ggrepel)
library(fontawesome)
library(kableExtra)
library(huxtable)
library(formatR)
```

# \faUniversity\acvHeaderIconSep\ Education

```{r education}
tribble(
  ~ Degree,
  ~ Year,
  ~ Institution,
  "Doctor of Philosophy (Ecology & Evolution)","2022–present","Australian National University",
  "Master of Scientific Studies (Biodiversity Science)","2019–2021","University of New England",
  "Graduate Certificate in Science (Biodiversity Science)","2018–2019","University of New England",
  "Bachelor of Music (Performance: Classical Voice)","2014–2017","Sydney Conservatorium of Music",
  "Bachelor of Arts in Communication (Media Arts and Production)","2011–2013","University of Technology Sydney",
) %>%
  detailed_entries(
    what = Institution,
    with = Degree,
    where = Year
  )
```

# \faIcon{money-bill-wave}\acvHeaderIconSep\ Grants
```{r}
tribble(
  ~Year, ~Name, ~Institution, ~Supp, ~Amount,
  '2022', 'RSB Seed Funding Grant', 'Australian National University, Research School of Biology', 'Evolutionary and population ecology of Pterostylis (Orchidaceae) and their fungal symbionts (Ceratobasidium, Ceratobasidiaceae)', '$15,000',
  '2022', 'AOF Research Grant 348/22', 'Australian Orchid Foundation', 'The evolution and diversification of the Australian Diurideae: Understanding the influence of genome size and chromosome number ', '$10,000',
  '2022', 'Hansjörg Eichler Scientific Research Fund','Australasian Systematic Botany Society', 'An integrative taxonomic study of the Pterostylis macrosepala (D.L.Jones) G.N.Backh. complex (Orchidaceae; Pterostylidinae)','$5,000',
  '2020', "N.C.W. Beadle Scholarship in Botany", "University of New England",NA,'$1,000',
 ) %>% 
  detailed_entries(
    where = Year,
    with = Name, 
    what = Institution,
    why = Supp,
    when = Amount
  ) 
```
# \faIcon{award}\acvHeaderIconSep\ Awards & Scholarships
```{r}
tribble(
  ~ award, ~ year,
  "ANU Research School of Biology 3-Minute Thesis (3MT) Competition: People's Choice Award","2022",
  "ANU Research School of Biology 3-Minute Thesis (3MT) Competition: Runner Up Prize","2022",
  "Australian Government Research Training Program Scholarship (2022–2025)","2022",
  "University of New England Vice-Chancellor's Scholar", "2021",
  "Berlin Opera Academy Robert Earl White Memorial Scholarship", "2017",
  "Berlin Opera Academy Elizabeth Luxon Memorial Scholarship", "2017",
  "Pacific Opera Young Artist Scholarship", "2017", 
  "Estivo European Chamber Music Summer School Scholarship", "2016",
  "Best Comedic Film: Tampa Bay Underground Film Festival", "2015",
  "Best Short Film: Melbourne Underground Film Festival", "2014",
  "Firstdraft Gallery Emerging Writers Residency", "2012",
  "University of Sydney Kathleen Garnham Laurence Prize for Fine Arts", "2010",
) %>% 
  brief_entries(award, year, .protect = FALSE)
```

# \faIcon{book}\acvHeaderIconSep\ Peer-Reviewed Publications

**O’Donnell RP**, Bruhl JJ, Telford IR, Wilson TC, Zimmer H, Taseski GM, Andrew RL (accepted 2023) Molecular and morphological analyses support recognition of *Prostanthera volucris* (Lamiaceae), a new species from the Central Tablelands of New South Wales. *Australian Systematic Botany*.

[**O’Donnell RP**, Wilson TC, Andrew RL, Telford IR, Taseski GM, Zimmer H, Bruhl JJ (2021) Molecular phylogenetic analysis of the *Prostanthera phylicifolia* (Lamiaceae) assemblage resolves relationships of the ’Critically Endangered’ *P. gilesii* and other putative new species. *Telopea* 24, 359–375. doi:10.7751/telopea15561.](https://openjournals.library.sydney.edu.au/index.php/TEL/article/view/15561)

# \faIcon{book-open}\acvHeaderIconSep\ Preprints

[**O’Donnell RP**, Bruhl JJ, Telford IR, Wilson TC, Zimmer H, Taseski GM, Andrew RL (accepted 2023) Molecular and morphological analyses support recognition of *Prostanthera volucris* (Lamiaceae), a new species from the Central Tablelands of New South Wales. doi:doi.org/10.1101/2021.12.21.473648.](https://doi.org/10.1101/2021.12.21.473648)

# \faIcon{file-alt}\acvHeaderIconSep\ Other Publications

[**O’Donnell RP** (2022) Book Review: Presenting Science Concisely - Bruce Kirchoff. Australasian Systematic Botany Society Newsletter. 190: 27–28.](https://asbs.org.au/newsletter/pdf/22-mar-190.pdf)

[**O’Donnell RP** (2022) *Love Thy Neighbour* Science Write Now #6: Natural History and Historians](https://www.sciencewritenow.com/essays-craft-memoir/love-thy-neighbour)

[**O’Donnell RP** (2021) *Love Thy Neighbour* Boundless Writers Festival 2021](https://www.sciencewritenow.com/essays-craft-memoir/love-thy-neighbour)

[**O’Donnell RP** (2021) Selling systematics with storytelling: solving taxonomy’s marketing problem. Australasian Systematic Botany Society Newsletter. 188: 29–30.](https://www.asbs.org.au/newsletter/pdf/21-sep-188.pdf)

[**O’Donnell RP** (2012) *John A Douglas - Body Fluid - The Seven Cycles* Exhibition essay - Chalkhorse Gallery](https://rpodonnell.github.io/cv/JAD_BODY_FLUIDfinal.pdf)

[**O’Donnell RP** (2012) *James Oram - Moments of Must Have* Exhibition essay - Chalkhorse Gallery](https://rpodonnell.github.io/cv/JamesOramMomentsofmusthave_RS.pdf)

# \faIcon{users}\acvHeaderIconSep\ Conference Presentations

**O’Donnell RP**, Wong DJ, Peakall R, Phillips RD, Linde CC (2022) "Detangling the Diurideae: Phylogenomics and
fungal symbionts provide an updated evolutionary framework". Australasian Evolution Society 2022, 14-16
December 2022.

**O’Donnell RP**, Wong DJ, Peakall R, Phillips RD, Linde CC (2022) "Detangling the Diurideae: Phylogenomics and
fungal symbionts provide an updated evolutionary framework". Australasian Systematic Botany Society EMCR
Conference 2022, 15-16 November 2022.

**O’Donnell RP**, Andrew RL, Telford IR, Wilson TC, Zimmer H, Taseski GM, Bruhl JJ (2021) "Morphological and
molecular evidence aid resolution of *Prostanthera phylicifolia s. l.* (Lamiaceae)". Australasian Systematic Botany
Society Annual Conference 2021, 12-16 July 2021. *Runner up: Pauline Ladiges Prize for best student presentation.*

# \faIcon{microphone-alt}\acvHeaderIconSep\ Other Presentations & Panels

[**Presenter:** *'Walks & Talks: Orchids From Australia & Abroad'* 13/08/2022](https://www.instagram.com/p/ChLqF9UuGza)

[**Presenter:** *'Rare Plants - Large and Small' with Costa Georgiadis* 12/05/2021](https://www.facebook.com/CostasWorld/videos/491418699340504/)

**Panelist:** *Reel Science: Plants - Sydney Science Trail/National Science Week* 21/08/2021

# \faIcon{chalkboard-teacher}\acvHeaderIconSep\ Teaching
## Australian National University
```{r teaching}
tribble(
  ~ title, ~ code, ~ semester,
  "Data Science for Biologists", "BIOL3207/BIOL6207","2022 S2",
  "Evolution", "BIOL2114/BIOL6114","2022 S2",
) %>% 
  brief_entries(glue::glue("\\textbf{<code>}: <title>", .open = "<", .close = ">"), semester, .protect = FALSE)
```

# \faIcon{tv}\acvHeaderIconSep\ Media

[**Radio Interview:** *ABC Radio Evenings with Christine Anu* 21/8/2021](https://soundcloud.app.goo.gl/qHSz4CY8nj2adUtb7)

[**Podcast Interview:** *Royal Botanic Garden Sydney 'Branch Out' Podcast - Starting in Science*](https://www.rbgsyd.nsw.gov.au/Science/Branch-Out/Starting-in-Science)

[**Interview:** *The Music, With Sylvie*](https://rpodonnell.github.io/cv/sylvie_interview_2020.pdf)

[**Interview:** *University of New England, #StudyLifeUNE*](https://www.facebook.com/UniNewEngland/posts/10158232724220926)

# \faIcon{palette}\acvHeaderIconSep\ Exhibitions

2021 [**The Margaret Flockton Award**](https://www.rbgsyd.nsw.gov.au/Science/Botanical-Illustration/The-Margaret-Flockton-Award-21)

# \faIcon{user-plus}\acvHeaderIconSep\ Professional Memberships
2020–present **Australasian Systematic Botany Society**

