---
name: Ryan P. 
surname: O'Donnell
date: "`r format(Sys.time(), '%B, %Y')`"
position: PhD Student
address: Research School of Biology, Australian National University
email: ryan.odonnell@anu.edu.au
website: rpodonnell.github.io
github: rpodonnell
linkedin: rpodonnell
twitter: rpodonnell_
headcolor: "414141"
fontawesome: yes
fontsize: 10
output:
  vitae::awesomecv:
    keep_tex: true
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(vitae)
library(ggplot2)
library(dplyr)
library(ggrepel)
library(fontawesome)
library(kableExtra)
library(huxtable)
library(formatR)
library(readxl)
library(glue)

#create function to read in excel spreadsheet of cv data
readExcelSheets <- function(filename){
  # read all sheets in .xlsx 
  all <- readxl::excel_sheets(filename)
  # import each sheet into a list using readxl::read_excel
  list <- lapply(all, function(x) readxl::read_excel(filename, sheet = x))
  # save sheet name for each sheet (list)
  names(list) <- all
  # breaks up list and creates a dataframe for each sheet with df names matching sheet names
  list2env(list, envir = .GlobalEnv)
}

filename <- here::here("RPO_vitae_data.xlsx")
readExcelSheets(filename)
```

# \faUniversity\acvHeaderIconSep\ Education

```{r education}
education %>%
  detailed_entries(
    what = institution,
    with = degree,
    where = year
  )
```
# \faIcon{brain}\acvHeaderIconSep\ Skills

```{r}
skills_formatted <- skills %>% 
  group_by(category) %>% 
  summarize(skills = glue_collapse(skill, sep = " $\\bullet$ "))
```

```{r}
skills_formatted %>% 
  detailed_entries(glue::glue("\\textbf{<category>}: <skills>", .open = "<", .close = ">"),  .protect = FALSE)
```

# \faIcon{money-bill-wave}\acvHeaderIconSep\ Grants
```{r}
grants %>% 
  detailed_entries(
    where = year,
    with = name, 
    what = institution,
    why = supp,
    when = amount
  ) 
```


# \faIcon{book}\acvHeaderIconSep\ Peer-Reviewed Publications

[**O’Donnell RP**, Bruhl JJ, Telford IR, Wilson TC, Zimmer H, Taseski GM, Andrew RL (2023) Molecular and morphological analyses support recognition of *Prostanthera volucris* (Lamiaceae), a new species from the Central Tablelands of New South Wales. *Australian Systematic Botany* 36, 1:1–20. doi:10.1071/SB22017.](https://doi.org/10.1071/SB22017)

[**O’Donnell RP**, Wilson TC, Andrew RL, Telford IR, Taseski GM, Zimmer H, Bruhl JJ (2021) Molecular phylogenetic analysis of the *Prostanthera phylicifolia* (Lamiaceae) assemblage resolves relationships of the ’Critically Endangered’ *P. gilesii* and other putative new species. *Telopea* 24, 359–375. doi:10.7751/telopea15561.](https://openjournals.library.sydney.edu.au/index.php/TEL/article/view/15561)

# \faIcon{book-open}\acvHeaderIconSep\ Preprints

[**O’Donnell RP**, Bruhl JJ, Telford IR, Wilson TC, Zimmer H, Taseski GM, Andrew RL (accepted 2023) Molecular and morphological analyses support recognition of *Prostanthera volucris* (Lamiaceae), a new species from the Central Tablelands of New South Wales. doi:doi.org/10.1101/2021.12.21.473648.](https://doi.org/10.1101/2021.12.21.473648)

# \faIcon{file-alt}\acvHeaderIconSep\ Other Publications

[**O’Donnell RP** (2022) Book Review: Presenting Science Concisely - Bruce Kirchoff. Australasian Systematic Botany Society Newsletter. 190: 27–28.](https://asbs.org.au/newsletter/pdf/22-mar-190.pdf)

[**O’Donnell RP** (2022) *Love Thy Neighbour* Science Write Now #6: Natural History and Historians](https://www.sciencewritenow.com/essays-craft-memoir/love-thy-neighbour)

[**O’Donnell RP** (2021) *Love Thy Neighbour* Boundless Writers Festival 2021](https://www.sciencewritenow.com/essays-craft-memoir/love-thy-neighbour)

[**O’Donnell RP** (2021) Selling systematics with storytelling: solving taxonomy’s marketing problem. Australasian Systematic Botany Society Newsletter. 188: 29–30.](https://www.asbs.org.au/newsletter/pdf/21-sep-188.pdf)

[**O’Donnell RP** (2012) *John A Douglas - Body Fluid - The Seven Cycles* Exhibition essay - Chalkhorse Gallery](https://rpodonnell.github.io/cv/JAD_BODY_FLUIDfinal.pdf)

[**O’Donnell RP** (2012) *James Oram - Moments of Must Have* Exhibition essay - Chalkhorse Gallery](https://rpodonnell.github.io/cv/JamesOramMomentsofmusthave_RS.pdf)

# \faIcon{users}\acvHeaderIconSep\ Conference Presentations

**O’Donnell RP**, Wong DJ, Peakall R, Phillips RD, Linde CC (2022) "Detangling the Diurideae: Phylogenomics and
fungal symbionts provide an updated evolutionary framework". Australasian Evolution Society 2022, 14-16
December 2022.

**O’Donnell RP**, Wong DJ, Peakall R, Phillips RD, Linde CC (2022) "Detangling the Diurideae: Phylogenomics and
fungal symbionts provide an updated evolutionary framework". Australasian Systematic Botany Society EMCR
Conference 2022, 15-16 November 2022.

**O’Donnell RP**, Andrew RL, Telford IR, Wilson TC, Zimmer H, Taseski GM, Bruhl JJ (2021) "Morphological and
molecular evidence aid resolution of *Prostanthera phylicifolia s. l.* (Lamiaceae)". Australasian Systematic Botany
Society Annual Conference 2021, 12-16 July 2021. *Runner up: Pauline Ladiges Prize for best student presentation.*

# \faIcon{microphone-alt}\acvHeaderIconSep\ Other Presentations & Panels
**Invited Speaker & Panelist:** *'An Evening With 500 Queer Scientists'* World Pride 2023

[**Presenter:** *'Walks & Talks: Orchids From Australia & Abroad'* 13/08/2022](https://www.instagram.com/p/ChLqF9UuGza)

[**Presenter:** *'Rare Plants - Large and Small' with Costa Georgiadis* 12/05/2021](https://www.facebook.com/CostasWorld/videos/491418699340504/)

**Panelist:** *Reel Science: Plants - Sydney Science Trail/National Science Week* 21/08/2021

# \faIcon{chalkboard-teacher}\acvHeaderIconSep\ Teaching
## Australian National University
```{r teaching}
teaching %>% 
  brief_entries(glue::glue("\\textbf{<code>}: <title>", .open = "<", .close = ">"), semester, .protect = FALSE)
```

# \faIcon{award}\acvHeaderIconSep\ Awards & Scholarships
```{r}
awards %>% 
  brief_entries(award, year, .protect = FALSE)
```

# \faIcon{tv}\acvHeaderIconSep\ Media
[**Radio Interview:** *ABC Radio, Science Friction with Natasha Mitchell 'World Pride 2023 - Love Your Nature'* 17/02/2023](https://www.abc.net.au/radionational/programs/sciencefriction/world-pride-queer-science-botany-plants/101948162)

[**Radio Interview:** *ABC Radio Evenings with Christine Anu* 21/8/2021](https://soundcloud.app.goo.gl/qHSz4CY8nj2adUtb7)

[**Podcast Interview:** *Royal Botanic Garden Sydney 'Branch Out' Podcast - Starting in Science*](https://www.rbgsyd.nsw.gov.au/Science/Branch-Out/Starting-in-Science)

[**Interview:** *The Music, With Sylvie*](https://rpodonnell.github.io/cv/sylvie_interview_2020.pdf)

[**Interview:** *University of New England, #StudyLifeUNE*](https://www.facebook.com/UniNewEngland/posts/10158232724220926)

# \faIcon{palette}\acvHeaderIconSep\ Exhibitions

2021 [**The Margaret Flockton Award**](https://www.rbgsyd.nsw.gov.au/Science/Botanical-Illustration/The-Margaret-Flockton-Award-21)

# \faIcon{user-plus}\acvHeaderIconSep\ Professional Memberships
2020–present **Australasian Systematic Botany Society**
