---
name: Ryan P. 
surname: "O'Donnell"
date: "`r format(Sys.time(), '%B, %Y')`"
position: Mycologist & Botanist | PhD Candidate
address: Research School of Biology, Australian National University
email: ryan.odonnell@anu.edu.au
website: rpodonnell.github.io
github: rpodonnell
linkedin: rpodonnell
twitter: rpodonnell.bsky.social
headcolor: "414141"
fontawesome: yes
fontsize: 10
output:
  vitae::awesomecv:
    keep_tex: true
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(vitae)
library(ggplot2)
library(dplyr)
library(ggrepel)
library(fontawesome)
library(kableExtra)
library(huxtable)
library(formatR)
library(readxl)
library(glue)

#create function to read in excel spreadsheet of cv data
readExcelSheets <- function(filename){
  # read all sheets in .xlsx 
  all <- readxl::excel_sheets(filename)
  # import each sheet into a list using readxl::read_excel
  list <- lapply(all, function(x) readxl::read_excel(filename, sheet = x))
  # save sheet name for each sheet (list)
  names(list) <- all
  # breaks up list and creates a dataframe for each sheet with df names matching sheet names
  list2env(list, envir = .GlobalEnv)
}

filename <- here::here("RPO_vitae_data.xlsx")
readExcelSheets(filename)
```

# \faUniversity\acvHeaderIconSep\ Education

```{r education}
education %>%
  detailed_entries(
    what = institution,
    with = degree,
    where = year
  )
```
# \faIcon{brain}\acvHeaderIconSep\ Skills

```{r}
skills_formatted <- skills %>% 
  group_by(category) %>% 
  summarize(skills = glue_collapse(skill, sep = " $\\bullet$ "))
```

```{r}
skills_formatted %>% 
  detailed_entries(glue::glue("\\textbf{<category>}: <skills>", .open = "<", .close = ">"),  .protect = FALSE)
```

# \faIcon{money-bill-wave}\acvHeaderIconSep\ Grants
```{r}
grants %>% 
  detailed_entries(
    where = year,
    with = name, 
    what = institution,
    why = supp,
    when = amount
  ) 
```


# \faIcon{book}\acvHeaderIconSep\ Peer-Reviewed Publications

## First-Author

**O’Donnell RP**, Linde CC, May TW (in press) Rise up, *Rhizoctonia*: moving to one fungus, one name in the Ceratobasidiaceae (Agaricomycetes; Cantharellales). *Persoonia*. 

[**O’Donnell RP**, Wong DJ, Peakall R, Phillips RD, Linde CC (2024) *Discordance Down Under*: Combining phylogenomics & fungal symbioses to detangle difficult nodes in a diverse tribe of Australian terrestrial orchids. *Systematic Biology*, syae070. doi:10.1093/sysbio/syae070.](https://academic.oup.com/sysbio/advance-article/doi/10.1093/sysbio/syae070/7918489?utm_source=authortollfreelink&utm_campaign=sysbio&utm_medium=email&guestAccessKey=18bacc24-7f10-439a-94f4-3030811184af) 

[**O’Donnell RP**, Bruhl JJ, Telford IR, Wilson TC, Zimmer H, Taseski GM, Andrew RL (2023) Molecular and morphological analyses support recognition of *Prostanthera volucris* (Lamiaceae), a new species from the Central Tablelands of New South Wales. *Australian Systematic Botany* 36, 1:1–20. doi:10.1071/SB22017.](https://doi.org/10.1071/SB22017)

[**O’Donnell RP**, Wilson TC, Andrew RL, Telford IR, Taseski GM, Zimmer H, Bruhl JJ (2021) Molecular phylogenetic analysis of the *Prostanthera phylicifolia* (Lamiaceae) assemblage resolves relationships of the ’Critically Endangered’ *P. gilesii* and other putative new species. *Telopea* 24, 359–375. doi:10.7751/telopea15561.](https://doi.org/10.7751/telopea15561)

\pagebreak

## Co-Author

[Hyde KD ... Zvyagina E (2024) The 2024 Outline of Fungi and fungus-like taxa. *Mycosphere* 15, 1:5146–6239. doi:10.5943/mycosphere/15/1/25.](https://www.mycosphere.org/pdf/MYCOSPHERE_15_1_25.pdf)

[Hyde KD ... Zucconi L (2023) Global consortium for the classification of fungi and fungus-like taxa. *Mycosphere* 14, 1:1960–2012. doi:10.5943/mycosphere/14/1/23.](https://www.mycosphere.org/pdf/MYCOSPHERE_14_1_23-1.pdf)

# \faIcon{search}\acvHeaderIconSep\ Manuscripts In Review 

## First-Author

John EG$^†$, **O’Donnell RP**$^†$, Perkins J, Rubial M, Peakall R, Wong DCJ (under review - Molecular Biology and Evolution) Once in a blue moon: phylotranscriptomics reveals the unusual genetic basis of blue floral colour in the terrestrial orchid subtribe Caladeniinae (Diurideae; Orchidaceae).

$^†$Shared co-first authors.

# \faIcon{book-open}\acvHeaderIconSep\ Preprints

[**O’Donnell RP**, Bruhl JJ, Telford IR, Wilson TC, Zimmer H, Taseski GM, Andrew RL (accepted 2023) Molecular and morphological analyses support recognition of *Prostanthera volucris* (Lamiaceae), a new species from the Central Tablelands of New South Wales. doi:doi.org/10.1101/2021.12.21.473648.](https://doi.org/10.1101/2021.12.21.473648)

# \faIcon{file-alt}\acvHeaderIconSep\ Other Publications

[**O’Donnell RP** (2024) An integrative taxonomic study of the *Pterostylis macrosepala* (D.L.Jones) G.N.Backh. complex (Orchidaceae; Pterostylidinae) Hansjörg Eichler Scientific Research Fund Report. Australasian Systematic Botany Society Newsletter. 199: 5–11.](https://asbs.org.au/wp-content/uploads/2024/07/ASBSNewsletter_199-8July24-ONLINE.pdf#page=7)

[**O’Donnell RP** (2022) Book Review: Presenting Science Concisely - Bruce Kirchoff. Australasian Systematic Botany Society Newsletter. 190: 27–28.](https://asbs.org.au/newsletter/pdf/22-mar-190.pdf)

[**O’Donnell RP** (2022) *Love Thy Neighbour* Science Write Now #6: Natural History and Historians](https://www.sciencewritenow.com/essays-craft-memoir/love-thy-neighbour)

[**O’Donnell RP** (2021) *Love Thy Neighbour* Boundless Writers Festival 2021](https://www.sciencewritenow.com/essays-craft-memoir/love-thy-neighbour)

[**O’Donnell RP** (2021) Selling systematics with storytelling: solving taxonomy’s marketing problem. Australasian Systematic Botany Society Newsletter. 188: 29–30.](https://www.asbs.org.au/newsletter/pdf/21-sep-188.pdf)

# \faIcon{users}\acvHeaderIconSep\ Conference Presentations

**O’Donnell RP**, Wong DJ, Peakall R, Phillips RD, Linde CC (2024) "Fungal symbiont shifts inform subtribal relationships in terrestrial orchids". International Mycological Congress 2024, 11–15 August 2024. 

**O’Donnell RP**, Linde CC, May TW (2024) "Rise up, *Rhizoctonia*: moving to one fungus, one name in the Ceratobasidiaceae (Agaricomycetes; Cantharellales)" (Poster). International Mycological Congress 2024, 11–15 August 2024. 

**O’Donnell RP**, Linde CC, May TW (2023) "Rise up, *Rhizoctonia*: moving to one fungus, one name in the Ceratobasidiaceae (Agaricomycetes; Cantharellales)". Biosystematics 2023, 26–30 November 2023. 

**O’Donnell RP**, Wong DJ, Peakall R, Phillips RD, Linde CC (2022) "Detangling the Diurideae: Phylogenomics and
fungal symbionts provide an updated evolutionary framework". Australasian Evolution Society 2022, 14–16
December 2022.

**O’Donnell RP**, Wong DJ, Peakall R, Phillips RD, Linde CC (2022) "Detangling the Diurideae: Phylogenomics and
fungal symbionts provide an updated evolutionary framework". Australasian Systematic Botany Society EMCR
Conference 2022, 15–16 November 2022.

**O’Donnell RP**, Andrew RL, Telford IR, Wilson TC, Zimmer H, Taseski GM, Bruhl JJ (2021) "Morphological and
molecular evidence aid resolution of *Prostanthera phylicifolia s. l.* (Lamiaceae)". Australasian Systematic Botany
Society Annual Conference 2021, 12–16 July 2021. *Runner up: Pauline Ladiges Prize for best student presentation.*

# \faIcon{microphone-alt}\acvHeaderIconSep\ Other Presentations & Panels

**Panelist:** *Magic Mycelium* Bundanon Art Museum 09/03/2025

**Invited Speaker:** '*Discordance Down Under*: Combining phylogenomics & fungal symbioses to detangle difficult nodes in a diverse tribe of Australian terrestrial orchids' Australasian Mycological Society (AMS) Virtual Seminar Series 31/10/2024

**Invited Speaker & Panelist:** *'An Evening With 500 Queer Scientists'* World Pride 2023

[**Presenter:** *'Walks & Talks: Orchids From Australia & Abroad'* 13/08/2022](https://www.instagram.com/p/ChLqF9UuGza)

[**Presenter:** *'Rare Plants - Large and Small' with Costa Georgiadis* 12/05/2021](https://www.facebook.com/CostasWorld/videos/491418699340504/)

**Panelist:** *Reel Science: Plants - Sydney Science Trail/National Science Week* 21/08/2021

# \faIcon{chalkboard-teacher}\acvHeaderIconSep\ Teaching
## Australian National University
```{r teaching}
teaching %>% 
  brief_entries(glue::glue("\\textbf{<code>}: <title>", .open = "<", .close = ">"), semester, .protect = FALSE)
```
# \faIcon{award}\acvHeaderIconSep\ Awards & Scholarships
```{r}
awards %>% 
  brief_entries(award, year, .protect = FALSE)
```

# \faIcon{tv}\acvHeaderIconSep\ Media
[**Radio Interview:** *Fuzzy Logic 2XXfm, Live at Floriade 2024* 15/09/2024](https://www.2xxfm.org.au/shows/fuzzy-logic/)

[**Radio Interview:** *ABC Radio, Science Friction with Natasha Mitchell 'World Pride 2023 - Love Your Nature'* 17/02/2023](https://www.abc.net.au/radionational/programs/sciencefriction/world-pride-queer-science-botany-plants/101948162)

[**Radio Interview:** *ABC Radio Evenings with Christine Anu* 21/8/2021](https://soundcloud.app.goo.gl/qHSz4CY8nj2adUtb7)

[**Podcast Interview:** *Royal Botanic Garden Sydney 'Branch Out' Podcast - Starting in Science*](https://www.rbgsyd.nsw.gov.au/Science/Branch-Out/Starting-in-Science)

[**Interview:** *The Music, With Sylvie*](https://rpodonnell.github.io/cv/sylvie_interview_2020.pdf)

[**Interview:** *University of New England, #StudyLifeUNE*](https://www.facebook.com/UniNewEngland/posts/10158232724220926)

# \faIcon{palette}\acvHeaderIconSep\ Exhibitions

2021 [**The Margaret Flockton Award**](https://www.rbgsyd.nsw.gov.au/Science/Botanical-Illustration/The-Margaret-Flockton-Award-21)

# \faIcon{user-plus}\acvHeaderIconSep\ Professional Memberships
2023–present **Australasian Mycological Society** \
2020–present **Australasian Systematic Botany Society**
